### 2024-08-22 ms.qmd
Updates

```{r, packages}
#| label: packages
pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, forcats, MASS,
fitdistrplus, DHARMa)
```

@@

_Table 1. Estimates of the effects of temperature, CORT, and their interaction on latency, choice, and interest shown for the higher amount of food in each of the numerical discrimination tests. The table shows the comparissons for each predictor and the p~mcmcm~ value of the comparissons. In bold, the estimates with p~mcmc~ < 0.05._

@@

#| tbl-cap: "Estimates of the effects of each treatment and their interaction on the latency, choice, and interest shown for the higher amount of food in each of the numerical discrimination tests. The table shows the comparissons for each predictor and the p~mcmcm~ value of the comparissons. In bold, the estimates with p~mcmc~ < 0.05."

@@

    effect_temp <- format_dec(mean(c(Hot_CORT, Hot_Control)) - mean(c(Cold_CORT, Cold_Control)), 2)
    effect_hormone <- format_dec(mean(c(Hot_Control, Cold_Control)) - mean(c(Hot_CORT, Cold_CORT)), 2)
    interaction <- format_dec((mean(Hot_Control) - mean(Cold_Control)) - (mean(Hot_CORT) - mean(Cold_CORT)), 2)

@@

  mutate(results = paste(Effect, "(p", pmcmc, ")")) %>%

@@

 font.size = 10,
 layout = "autofit")

@@

    hline(i = c(3,6), j = c(1:7), part = "body") # To make some horizontal lines 

@@

```{r, fig-results}
#| label: fig-results
#| fig.cap: "" 
```

@@

#### Preliminary results

@@

```{r, summary_org}
#| label: summary_org
#
## Get the summary of the posteriors to get the estimates of each parameter of the model
sum <- summary(posteriors)
## Extract the values of the summary
sum_df <- as.data.frame(sum) %>%
  dplyr::select(-mad) %>%
  filter(!str_detect(variable, "^r_"))
```

@@

_Table S2.- Estimated mean probability of choosing first the higher amount (Choice) and the mean interest for the higher amount of food (Interest) per treatment group for each of the numerical tests performed. p indicates the p~mcmcm~ value (p) of testing the hypothesis Choice ≠ 0.5, and Interest ≠ 0, which would indicate a preference towards one of choices (> towards higher amounts, < towards lower amounts) of the comparissons._

@@

  pivot_wider(names_from = Test, values_from = c(Effect, pmcmc), names_prefix = "") %>%
  dplyr::select(Variable, Treatment, 
                Effect_1VS4, pmcmc_1VS4,
                Effect_1VS3, pmcmc_1VS3,
                Effect_2VS4, pmcmc_2VS4,
                Effect_2VS3, pmcmc_2VS3,
                Effect_3VS4, pmcmc_3VS4)

@@

    add_header_row(values = c("", "1VS4", "1VS3", "2VS4", "2VS3", "3VS4"), colwidths = c(2, 2, 2, 2, 2, 2)) %>%
    add_header_row(values = c("", "Tests"), colwidths = c(2, 10)) %>%
    flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
    flextable::compose(i = 3, j = c(3,5,7,9,11), value = as_paragraph("Est. mean"), part = "head") %>% 
    flextable::compose(i = 3, j = c(4,6,8,10,12), value = as_paragraph("p"), part = "head") %>% 
    hline(i = 4, j = c(1:12), part = "body") %>% # To make some horizontal lines
    vline(i = c(1:8), j = c(4,6,8,10), part = "body") %>% # To make some vertical lines
    vline(i = c(2,3), j = c(4,6,8,10), part = "head") 

@@

_Table S3.- Number of individuals per treatment that chose the right (R) or left (L) side in each of the numerical tests. p-value indicates the result of the binomial test comparing the number of choices between sides._
```{r, tbl-sides}
#| label: tbl-sides
#| tbl-cap: "Number of individuals per treatment that chose the right (R) or left (L) side in each of the numerical tests. p-value indicates the result of the binomial test comparing the number of choices between sides."
source(here("R", "func.R"))
#
# 1) MAKING THE DF FOR THE TABLE
data_sides <- data_num %>%
  group_by(trt, test_type) %>% # Group by treatment and test
  summarise(
    right_choices = sum(side_choice == "Right", na.rm = TRUE),
    left_choices = sum(side_choice == "Left", na.rm = TRUE),
  ) %>% # Count the number of correct choices
  rowwise() %>%  # Ensure that mutate works row by row
  mutate(
    total_choices = right_choices + left_choices,  # Calculate total choices
    p_value = format_dec(binom.test(right_choices, total_choices)$p.value, 2)  # Perform binom test
  ) %>% # Test for differences between sides
  ungroup() %>%  # Remove rowwise grouping
  mutate(choices_Right_Left_p = paste0("R = ", right_choices, " | L = ", left_choices, " , p = ", p_value), # Create a column with the choices
        trt = recode(trt, 
                 "B_23" = "CORT-Cold (n = 20)", 
                 "A_23" = "Control-Cold (n = 20)", 
                 "B_28" = "CORT-Hot (n = 20)", 
                 "A_28" = "Control-Hot (n = 20)")) %>% # To order the treatments
  dplyr::select(trt, test_type, choices_Right_Left_p) %>% # Remove unused columns
  pivot_wider(names_from = test_type, values_from = c(choices_Right_Left_p)) %>% # To split between tests
data.frame()
#
# 2) MAKING THE TABLE
#
# Split the table_data df by task
sides_table <- flextable(data_sides) %>%
  compose(j = 1, value = as_paragraph(""), part = "header") %>%
  compose(j = 2, value = as_paragraph("1 VS 4"), part = "header") %>%
  compose(j = 3, value = as_paragraph("1 VS 3"), part = "header") %>%
  compose(j = 4, value = as_paragraph("2 VS 4"), part = "header") %>%
  compose(j = 5, value = as_paragraph("2 VS 3"), part = "header") %>%
  compose(j = 6, value = as_paragraph("3 VS 4"), part = "header") %>%
  set_table_properties( width = 0.9, layout = "autofit") %>%
  align(align = "center", part = "all")
sides_table
```

>>>>

```{r, packages}
#| label: packages
pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, forcats, MASS,
fitdistrplus, ggh4x, PupillometryR, cowplot, png, grid, remotes, ggthemes)
```

@@

```{r, fig-results}
#| label: fig-results
#| fig.cap: "Mean estimates of loglatency (Latency), the probability of choosing first the larger number of crickets (Choice), and the mean estimated interest for the larger number of crickets (Interest) per each of the treatments for each of the numerical tests performed. The x-axis represents the estimate, and in the y-axis are the density of the estimates. The different colours indicate the different treatments. Points and bars represent the mean and standard deviation of the mean of the estimates, respectively. Vertical dashed lines in Choice and Interest graphs indicate p = 0.5 and int = 0, respectively."
#
source(here("R", "func.R"))
#
#### A) Organise the df used for both parts of the figure for each variable
#
# First the df for violin plots for each variable using df_violin_plot function from func.r
df_viol_lat <- df_violin_plot("lat")
df_viol_choice <- df_violin_plot("choice")
df_viol_int <- df_violin_plot("int")
#
# Second the df for the points and bars plot for each variable using df_bars_plot function from func.r
df_bars_lat <- df_bars_plot("lat")
df_bars_choice <- df_bars_plot("choice")
df_bars_int <- df_bars_plot("int")
#
#### B) Make the plots for each variable using plotting function from func.r
#
fig_lat <- plotting("lat")
fig_choice <- plotting("choice")
fig_int <- plotting("int")
#
#### C) Combine the plots and make final figure
fig_results <- plot_grid(fig_lat, fig_choice, fig_int, ncol = 1)
ggsave("./output/figures/fig_results.png", plot=fig_results, width = 25, height = 25, units = "cm", dpi = 600)
knitr::include_graphics("./output/figures/fig_results.png")
```

_Table 1. Effects of temperature, CORT, and their interaction on latency, choice, and interest shown for the higher amount of food in each of the numerical discrimination tests. The table shows the comparissons for each predictor (Temperature = [meanHot - meanCold]; Hormone = [meanControl - meanCORT]; Interaction = [(meanHot-Control - meanHot-CORT) - (meanCold-Control - meanCold-CORT)]) and the p~mcmcm~ value of the comparisons. In bold, the effects where p~mcmc~ < 0.05._

@@

#| tbl-cap: "Effects of temperature, CORT, and their interaction on latency, choice, and interest shown for the higher amount of food in each of the numerical discrimination tests. The table shows the comparissons for each predictor (Temperature = [meanHot - meanCold]; Hormone = [meanControl - meanCORT]; Interaction = [(meanHot-Control - meanHot-CORT) - (meanCold-Control - meanCold-CORT)]) and the p~mcmcm~ value of the comparisons. In bold, the effects where p~mcmc~ < 0.05."

@@

    effect_temp <- format_dec(mean(c(Hot_CORT, Hot_Control)) - mean(c(Cold_CORT, Cold_Control)), 1)
    effect_hormone <- format_dec(mean(c(Hot_Control, Cold_Control)) - mean(c(Hot_CORT, Cold_CORT)), 1)
    interaction <- format_dec((mean(Hot_Control) - mean(Cold_Control)) - (mean(Hot_CORT) - mean(Cold_CORT)), 1)

@@

  mutate(results = trimws(paste0(Effect, " (p", pmcmc,")"))) %>%

@@

 font.size = 9)

@@

    hline(i = c(3,6), j = c(1:7), part = "body") %>% # To make some horizontal lines 
    set_table_properties(layout = "autofit", width = 1)

@@

@@

#### Model results

@@

```{r, summary_org}
#| label: summary_org
#
## Get the summary of the posteriors to get the estimates of each parameter of the model
sum <- summary(posteriors)
## Extract the values of the summary
sum_2 <- as.data.frame(sum) %>%
  dplyr::select(-mad) %>%
  filter(!str_detect(variable, "^r_"))
sum_df <- sum_2 %>%
  mutate(across(where(is.numeric), ~ sprintf(paste0("%.", 2, "f"), .)))  
```

@@

_Table S2.- Estimated mean probability of choosing first the higher amount (Choice) and the mean interest for the higher amount of food (Interest) per treatment group for each of the numerical tests performed. p indicates the p~mcmcm~ value (p) of testing the hypothesis Choice ≠ 0.5, and Interest ≠ 0, which would indicate a preference towards one of choices (> towards higher amounts, < towards lower amounts) of the comparissons. In bold, the groups where p~mcmcm~ < 0.05_

@@

  pivot_wider(names_from = Variable, values_from = c(Effect, pmcmc), names_prefix = "") %>%
  dplyr::select(Test, Treatment, 
                Effect_Choice, pmcmc_Choice,
                Effect_Interest, pmcmc_Interest)

@@

    # Bold the cell containing "< 0.05" in the `pmcmc_Choice` column and the next cell
    bold(i = which(disc_df_final$pmcmc_Choice == "< 0.05"), j = "pmcmc_Choice", part = "body") %>%
    bold(i = which(disc_df_final$pmcmc_Choice == "< 0.05"), j = "Effect_Choice", part = "body") %>%
    bold(i = which(disc_df_final$pmcmc_Choice == "< 0.05"), j = "Treatment", part = "body") %>%
    # Bold the cell containing "< 0.05" in the `pmcmc_Interest` column and the next cell
    bold(i = which(disc_df_final$pmcmc_Interest == "< 0.05"), j = "pmcmc_Interest", part = "body") %>%
    bold(i = which(disc_df_final$pmcmc_Interest == "< 0.05"), j = "Effect_Interest", part = "body") %>%
    bold(i = which(disc_df_final$pmcmc_Interest == "< 0.05"), j = "Treatment", part = "body") %>%
    flextable::compose(i = c(2:4,6:8,10:12,14:16,18:20), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
    flextable::compose(i = 1, j = c(3,5), value = as_paragraph("Est. mean"), part = "head") %>% 
    flextable::compose(i = 1, j = c(4,6), value = as_paragraph("p"), part = "head") %>% 
    hline(i = c(4,8,12,16), j = c(1:6), part = "body") %>% # To make some horizontal lines
    vline(i = c(1:20), j = 4, part = "body") %>% # To make some vertical lines
    vline(i = 1, j = 4, part = "head") 

@@

_Table S3.- Number of individuals per treatment that chose the right (R) or left (L) side in each of the numerical tests. p-value indicates the result of the binomial test comparing the number of choices between sides. In bold, the groups where p-value < 0.05_
```{r, tbl-sides}
#| label: tbl-sides
#| tbl-cap: "Number of individuals per treatment that chose the right (R) or left (L) side in each of the numerical tests. p-value indicates the result of the binomial test comparing the number of choices between sides."
source(here("R", "func.R"))
#
# 1) MAKING THE DF FOR THE TABLE
data_sides <- data_num %>%
  group_by(trt, test_type) %>% # Group by treatment and test
  summarise(
    right_choices = sum(side_choice == "Right", na.rm = TRUE),
    left_choices = sum(side_choice == "Left", na.rm = TRUE),
  ) %>% # Count the number of correct choices
  rowwise() %>%  # Ensure that mutate works row by row
  mutate(
    total_choices = right_choices + left_choices,  # Calculate total choices
    p_value = format_dec(binom.test(right_choices, total_choices)$p.value, 2)  # Perform binom test
  ) %>% # Test for differences between sides
  ungroup() %>%  # Remove rowwise grouping
  mutate(choices_Right_Left_p = paste0("R = ", right_choices, " | L = ", left_choices, " , p = ", p_value), # Create a column with the choices
        trt = recode(trt, 
                 "B_23" = "CORT-Cold (n = 20)", 
                 "A_23" = "Control-Cold (n = 20)", 
                 "B_28" = "CORT-Hot (n = 20)", 
                 "A_28" = "Control-Hot (n = 20)")) %>% # To order the treatments
  dplyr::select(trt, test_type, choices_Right_Left_p) %>% # Remove unused columns
  pivot_wider(names_from = test_type, values_from = c(choices_Right_Left_p)) %>% # To split between tests
data.frame()
#
# 2) MAKING THE TABLE
#
# Split the table_data df by task
sides_table <- flextable(data_sides) %>%
  compose(j = 1, value = as_paragraph(""), part = "header") %>%
  compose(j = 2, value = as_paragraph("1 VS 4"), part = "header") %>%
  compose(j = 3, value = as_paragraph("1 VS 3"), part = "header") %>%
  compose(j = 4, value = as_paragraph("2 VS 4"), part = "header") %>%
  compose(j = 5, value = as_paragraph("2 VS 3"), part = "header") %>%
  compose(j = 6, value = as_paragraph("3 VS 4"), part = "header") %>%
  set_table_properties( width = 0.9, layout = "autofit") %>%
  align(align = "center", part = "all")
sides_table
```
